Democratizing Secure Two-Party Computation

### 2017-10-22 OaklandSubmission/ld.tex
finishing the text for languages and semantics

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & r &&\\
    \ftext{Circuit gate} & \kappa & ::= & r \mid \kw{in}^{m}_{j} \mid \kw{add}\:\kappa_{1}\:\kappa_{2} \mid \kw{gt}\:\kappa_{1}\:\kappa_{2}\\
    & & \mid & \kw{mux}\:\kappa\:\kappa_{1}\:\kappa_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \widetilde{w} & ::= & c \mid r\\
    \ftext{Value} & \widetilde{v} & ::= & \widetilde{w} \mid \kappa \mid [\overline{\widetilde{w}_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho}[x \mapsto \widetilde{v}]\\
    \ftext{Circuit} & \chi & ::= & \cdot \mid \kw{bind}\:\kappa\:r \mid \kw{out}\:\kappa \mid \kappa_{1}; \kappa_{2}
  \end{array}
  \]
\caption{Target runtime}
\label{fig:tgtruntime}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{S-SGt}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} >_{\mathcal{B}} \widetilde{e_{2}} \Downarrow \kw{gt}\:\kappa_{1}\:\kappa_{2}
               }\\\\
               \inferrule*[lab={\footnotesize{S-SCond}}]
               {
                 \forall i \in \{1, 2, 3\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \lcond{\mathcal{B}}{\widetilde{e_{1}}}{\widetilde{e_{2}}}{\widetilde{e_{3}}} \Downarrow \kw{mux}\:\kappa_{1}\:\kappa_{2}\:\kappa_{3}
               }
               \hspace{0.2cm}
    \inferrule*[lab={\footnotesize{S-Coerce}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{w}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e} \rhd m \Downarrow \widetilde{w} \rhd m
               }
               \\\\
               %% \inferrule*[lab={\footnotesize{S-Arr}}]
               %% {
               %%   \forall i \in \{0 \dots n - 1\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \widetilde{w_{i}}
               %% }
               %% {
               %%   \widetilde{\rho} \vdash [\overline{\widetilde{e_{i}}}]_{n} \Downarrow [\overline{\widetilde{w_{i}}}]_{n}
               %% }

@@

Figure~\ref{fig:tgtruntime} shows the runtime syntax. A wire id range
$r$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit. Circuit gates $\kappa$ are
$r$, input gates, \kw{add}, \kw{gt}, and \kw{mux} gates, and coerce
gates $\widetilde{w} \rhd m$. Target values $\widetilde{v}$ then
consist of base values $c$ and $r$, circuit gates $\kappa$, and arrays
of base values.

Figure~\ref{fig:tgtsem} shows the judgments for the target
semantics. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\widetilde{v}$. Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$, using an arithmetic add
gate, to $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Since our compiler
compiles secret add operations to arithmetic gates, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$ (we present the compilation rules
later in the section).

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{out}\:\kappa \Downarrow \widehat{\rho_{1}}, \widehat{\rho_{2}}; c
               }
\end{array}
  \]
\label{fig:cktsem}
\caption{Circuit semantics (selected rules)}
\end{figure}

>>>>

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & r &&\\
    \ftext{Circuit gate} & \kappa & ::= & r \mid \kw{in}^{m}_{j} \mid \kw{add}\:\kappa_{1}\:\kappa_{2} \mid \kw{gt}\:\kappa_{1}\:\kappa_{2}\\
    & & \mid & \kw{mux}\:\kappa\:\kappa_{1}\:\kappa_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \widetilde{w} & ::= & c \mid \kappa\\
    \ftext{Value} & \widetilde{v} & ::= & \widetilde{w} \mid [\overline{\widetilde{w}_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho}[x \mapsto \widetilde{v}]\\
    \ftext{Circuit} & \chi & ::= & \cdot \mid \kw{bind}\:\kappa\:r \mid \kw{out}\:\kappa \mid \chi_{1}; \chi_{2}
  \end{array}
  \]
\caption{Target runtime}
\label{fig:tgtruntime}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{S-SGt}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} >_{\mathcal{B}} \widetilde{e_{2}} \Downarrow \kw{gt}\:\kappa_{1}\:\kappa_{2}
               }\\\\
               \inferrule*[lab={\footnotesize{S-SCond}}]
               {
                 \forall i \in \{1, 2, 3\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \lcond{\mathcal{B}}{\widetilde{e_{1}}}{\widetilde{e_{2}}}{\widetilde{e_{3}}} \Downarrow \kw{mux}\:\kappa_{1}\:\kappa_{2}\:\kappa_{3}
               }
               \hspace{0.2cm}
    \inferrule*[lab={\footnotesize{S-Coerce}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{v}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e} \rhd m \Downarrow \widetilde{v} \rhd m
               }
               \\\\
               %% \inferrule*[lab={\footnotesize{S-Arr}}]
               %% {
               %%   \forall i \in \{0 \dots n - 1\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \widetilde{w_{i}}
               %% }
               %% {
               %%   \widetilde{\rho} \vdash [\overline{\widetilde{e_{i}}}]_{n} \Downarrow [\overline{\widetilde{w_{i}}}]_{n}
               %% }

@@

Figure~\ref{fig:tgtruntime} shows the runtime syntax. A wire id range
$r$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit. Circuit gates $\kappa$ are
$r$, input gates, \kw{add}, \kw{gt}, and \kw{mux} gates, and coerce
gates $\widetilde{w} \rhd m$. Target values $\widetilde{v}$ then
consist of base values $c$ and $\kappa$, and arrays of base values.

Figure~\ref{fig:tgtsem} shows the judgments for the target
semantics. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\widetilde{v}$. Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$, using an arithmetic add
gate, to $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Since our compiler
compiles secret add operations to arithmetic gates, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$ (we present the compilation rules
later in the section). Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the values from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the conditional ($\kappa_{1}$) and both the branches
($\kappa_{2}$ and $\kappa_{3}$). Rules {\sc{S-Coerce}} and
{\sc{S-Inp}} evaluate to the coerce and input gates respectively.

Statement evaluation $\widetilde{\rho} \vdash \widetilde{s} \Downarrow
\widetilde{\rho'}; \chi$ evaluates a target statement to produce a new
environment $\widetilde{\rho'}$, and a circuit $\chi$. $\chi$ (shown
in Figure~\ref{fig:tgtlang}) is either empty, \kw{bind}-ing of a
circuit gate $\kappa$ to range $r$, \kw{out} gate, or a sequence of
circuits. Rules ({\sc{S-DeclC}}), ({\sc{S-DeclCkt}}), and
({\sc{S-DeclCktArr}}) show the variable declaration cases. Rule
({\sc{S-DeclC}}) shows the case when $\widetilde{e}$ evaluates to
$\widetilde{v}$, where $\widetilde{v}$ is a constant or an array of
constants. In this case, the mapping $x \mapsto \widetilde{v}$ is
added to the environment, and the resulting circuit is empty. When
$\widetilde{e}$ evaluates to a circuit $\kappa$, rule
({\sc{S-DeclCkt}}) picks a fresh $r$, adds the mapping $x \mapsto r$
to the environment, and outputs the circuit
$\kw{bind}\:\kappa\:r$. Rule ({\sc{S-DeclCktA}}) is analogous for
$\widetilde{e}$ evaluating to an array of circuits. The variable
assignment rules (not shown in the figure) are similar. Rule
({\sc{S-WriteCkt}}) shows the case for writing to an array, where the
array contents are secret. Finally, rule ({\sc{S-Out}}) compiles to an
\kw{out} circuit.

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{out}\:\kappa \Downarrow \widehat{\rho_{1}}, \widehat{\rho_{2}}; c
               }
\end{array}
  \]
\caption{Circuit semantics (selected rules)}
\label{fig:cktsem}
\end{figure}

\subsubsection*{Circuit semantics} The target semantics produces a
circuit to compute over the secret data using an MPC protocol. With
our circuit semantics, we model the \emph{functional} aspect of the
protocol, parametrized by the sharing functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (opaque) strings $b$. The semantics of these strings is
given by pairs of encryption-decryption functions, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two string $b_{1}$ and $b_{2}$
(shares of the two parties), with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. We assume that the underlying MPC
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately.

The circuit semantics is shown in Figure~\ref{fig:cktsem} using the
judgments $\widehat{\rho_{1}}, \widehat{\rho_{1}} \vdash \kappa
\Downarrow b_{1}, b_{2}$, and $\widehat{\rho_{1}}, \widehat{\rho_{2}}
\vdash \chi \Downarrow \widehat{\rho_{1}'}, \widehat{\rho_{2}'}; O$,
where $\widehat{\rho_{1}}$ and $\widehat{\rho_{2}}$ are the circuit
environments of the two parties, mapping wire ranges $r$ to strings
$b$. Rule {\sc{C-Add}} evinces the pattern for evaluating circuit
gates $\kappa$. To evaluate $\kw{add}\:\kappa_{1}\:\kappa_{2}$, the
rule first evaluates $\kappa_{1}$ to $(b_{11}, b_{21})$ and
$\kappa_{2}$ to $(b_{12}, b_{22})$. Shares $(b_{11}, b_{21})$ are then
combined using $\mathcal{D_{\mathcal{A}}}$ to $n_{1}$, and similarly
$(b_{12}, b_{22})$ are combined to $n_{2}$. The final output of the
\kw{add} gate is then $\mathcal{E}_{\mathcal{A}}(n_{1} + n_{2})$. Note
that this is a functional description of how the \kw{add} gate
evaluates, of course, concretely $n_{1}$ and $n_{2}$ are not observed
by the parties. Rule {\sc{C-Coerce}} re-encrypts the shares using the
scheme for $m$. Coming to the evaluation of circuits, the evaluation
of \kw{bind} updates the mapping of $r$ in the input environments, and
the rule {\sc{C-Out}} outputs the clear value $c$ to the observations.

\subsubsection*{Compilation judgments}
